---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---

# ripestat

Query and Retrieve Data from the 'RIPEstat' 'API'

## Description

'RIPEstat' is a web-based interface that provides everything you ever 
wanted to know about 'IP' address space, 'Autonomous System Numbers' ('ASNs'), and 
related information for hostnames and countries in one place. Methods are provides to
query and retrieve data from the 'RIPEstat' 'API'.
    
## What's Inside The Tin

The following functions are implemented:

- `get_announced_prefixes`:	Announced Prefixes
- `get_country_resource_list`:	Country Resource List
- `get_dns_chain`:	DNS Chain
- `get_network_info`:	Network Info
- `reverse_dns_ip`:	Reverse DNS IP
- `whats_my_ip`:	What's My IP?

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/ripestat")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(ripestat)

# current verison
packageVersion("ripestat")

```

### Announced Prefixes

```{r}
str(get_announced_prefixes("AS3333")$data, 2)
```

### Country Resource List

```{r}
str(get_country_resource_list("MX")$data, 2)
```

### DNS Chain

```{r}
str(get_dns_chain("r-project.org")$data, 2)
```

### Network Info

```{r}
str(get_network_info("140.78.90.50")$data, 2)
```

### Reverse DNS IP

```{r}
str(reverse_dns_ip("193.0.6.139")$data, 2)
```

### What's My IP

```{r eval=FALSE}
whats_my_ip()
```
